Fusing Filters with Integer Linear Programming

### 2014-06-19 2014betterfusionforfilters/section/01-Introduction.tex
mention sequential & parallel

To compile the clusters found by our clustering technique into loops, we use data flow fusion~\cite{lippmeier2013flow}.
It improved on existing array fusion approaches~\cite{coutts2007streamfusion, keller2010repa} as it guarantees complete fusion into a single loop for programs that operate on the same size input data and contain no fusion-preventing dependencies between operators.

>>>>

To compile the clusters found by our clustering technique into sequential loops, we use data flow fusion~\cite{lippmeier2013flow}.
It improved on existing array fusion approaches~\cite{coutts2007streamfusion, keller2010repa} as it guarantees fusion into a single loop for programs that operate on the same size input data and contain no fusion-preventing dependencies between operators. 
Our clustering technique is also applicable to parallel loops.
